### 2015-08-06 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/Manual_coupling_AxiSEM_Specfem3D.tex
Final modifs in Axisem dir: 1 (big and last commit about this)
Buildbot ran the code beautifier.
Modif manual of coupling w Axisem

\noindent {\bf{Authors:}} V. Monteiller, C. Durochat

@@

@@

\item[\textbullet] KERNEL\_WAVEFIELDS   true
\item[\textbullet] KERNEL\_IBEG         0
\item[\textbullet] KERNEL\_IEND         4

@@

@@

\noindent run ./sub\_called\_batch\_for\_AxiSEM\_Curie\_CD.sh : submit the job on Curie.

@@

@@

\item[\textbullet] {\color{red} Check the file 'expand\_2D\_3D.par', cf THE PATHS IN THE 3 LAST LINES (normally, these are the only paths you to modify in the AxiSEM dir) !!} ==> Caution : for the tractions path (for example: /[...]/AxiSEM\_tractions/1/), the directory need to be created !!!! {\color{red} ~ ==>}

the script 'sub\_launch\_script\_for\_make\_+\_run\_expand2D3D\_and\_reformat\_Curie\_CD.sh' create a traction directory here:

@@

{\footnotesize 'EXAMPLES/coupling\_with\_EXTERNAL\_CODES/with\_AxiSEM/example\_1st\_for\_validation/DATA/AxiSEM\_tractions/1/', }

BUT, if you don't use this script or if you want to create another tractions dir, you have to create the directory yourself.

@@

\noindent Example :
\begin{verbatim}

input_box.txt
input_box_sem_cart.txt
32                          # number of AxiSEM mpi processes used in solver
90. 0.                      # source position (lat lon)
0.  60.                     # chunk center (lat lon)
1                           # number of axisem simus depends on moment tensor used
32                          # number of Specfem3D MPI processes
/[...]/example_1st_for_validation/MESH                          # Specfem MESH dir
/[...]/example_1st_for_validation/OUTPUT_FILES/DATABASES_MPI    # Specfem databases dir
/[...]/example_1st_for_validation/DATA/AxiSEM_tractions/1       # AxiSEM tractions dir

\end{verbatim}

\item[\textbullet] Check the file 'reformat.par'

\noindent Example :
\begin{verbatim}

10.         # = 1/DT, i.e. output sampling in Hz (time step that will use in Specfem3D simu)
710. 1800.  # begin time and end time (s.)

\end{verbatim}

@@

@@

\noindent You can launch the compilation (of expand\_2D\_3D and reformat) AND the execution of this two programs with the single script :

@@

@@

\noindent It will do the compilation, launch ./sub\_called\_batch\_for\_expand2D3D\_Curie\_CD.sh, and at the end, launch ./sub\_called\_batch\_for\_reformat\_Curie\_CD.sh $\Longleftarrow$ IMPORTANT : for the expand\_2D\_3D part, the number processes is arbitrary, BUT for the reformat part you have to configure the batch with the **SAME** number of processes that Specfem3D will use. Onefile is created by one process for one Spefem3D partion of domain.

@@

\noindent If you prefer you do this step by step :

\item[\textbullet] Go in {\scriptsize 'utils/EXTERNAL\_CODES\_coupled\_with\_SPECFEM3D/AxiSEM\_for\_SPECFEM3D/UTILS\_COUPLING\_SpecFEM'} to make the compilation.
\item[\textbullet] Go in NAME\_OF\_RESULTS\_DIR and type : run ../sub\_called\_batch\_for\_expand2D3D\_Curie\_CD.sh to submit expand\_2D\_3D
\item[\textbullet] Go in NAME\_OF\_RESULTS\_DIR and type : run ../sub\_called\_batch\_for\_reformat\_Curie\_CD.sh to submit reformat

>>>>

\noindent {\bf{Authors:}} C. Durochat, V. Monteiller

@@

\noindent We show the process of the coupling, for the example:

\noindent 'EXAMPLES/coupling\_with\_EXTERNAL\_CODES/with\_AxiSEM/example\_1st\_for\_validation', see the file 'README\_example\_details' for some particulars of this example.

\noindent There are other examples in 'EXAMPLES/coupling\_with\_EXTERNAL\_CODES/with\_AxiSEM/' with other set of parameters.

@@

\item[\textbullet] KERNEL\_WAVEFIELDS   true
\item[\textbullet] KERNEL\_IBEG         0
\item[\textbullet] KERNEL\_IEND         4
\item[\textbullet] KERNEL\_DUMPTYPE     coupling\_box

@@

\noindent (or 'sub\_launch\_script\_for\_run\_AxiSEM\_Curie\_CD\_VM.csh', it depends on examples)

@@

\noindent run ./sub\_called\_batch\_for\_AxiSEM\_Curie\_CD\textit{(\_VM)}.sh : submit the job on Curie.

@@

\noindent Go in {\scriptsize 'utils/EXTERNAL\_CODES\_coupled\_with\_SPECFEM3D/AxiSEM\_for\_SPECFEM3D/UTILS\_COUPLING\_SpecFEM'} and make the compilation (make clean ; make all).

\noindent Go in {\scriptsize 'utils/EXTERNAL\_CODES\_coupled\_with\_SPECFEM3D/AxiSEM\_for\_SPECFEM3D/AxiSEM\_modif\_for\_coupling\_with\_specfem/SOLVER'} :

@@

\item[\textbullet] {\color{red} Check the file 'expand\_2D\_3D.par', cf THE PATHS IN THE 3 LAST LINES (normally, these are the only paths you to modify in the AxiSEM dir) !!} ==> Caution : for the tractions path (for example: /[...]/AxiSEM\_tractions/1/), the directory need to be created !!!

@@

\noindent Example :
\begin{verbatim}
input_box.txt
input_box_sem_cart.txt
32                          # number of AxiSEM mpi processes used in solver
90. 0.                      # source position (lat lon)
0.  60.                     # chunk center (lat lon)
1                           # number of axisem simus depends on moment tensor used
32                          # number of Specfem3D MPI processes
/[...]/example_1st_for_validation/MESH                          # Specfem MESH dir
/[...]/example_1st_for_validation/OUTPUT_FILES/DATABASES_MPI    # Specfem databases dir
/[...]/example_1st_for_validation/DATA/AxiSEM_tractions/1       # AxiSEM tractions dir
\end{verbatim}

\item[\textbullet] Go in NAME\_OF\_RESULTS\_DIR and type : run ../sub\_called\_batch\_for\_expand2D3D\_Curie\_CD.sh to submit expand\_2D\_3D (the number processes is here arbitrary)

\item[\textbullet] At the end of expand\_2D\_3D, check the file 'StaLta.txt' to see at what time, the seismos begin to be non-zero. With this information, you can {\color{red} configure} begin time (corresponding to a little before the time when the values in 'StaLta.txt' begin to be non-zero) {\color{red} in the file 'reformat.par'}:

@@

\noindent Example :
\begin{verbatim}
10.         # = 1/DT, i.e. output sampling in Hz (time step that will use in specfem simu)
710. 1800.  # begin time and end time (s.) (corresponding to the SpecFEM simulation time)
\end{verbatim}

\item[\textbullet] Stay in NAME\_OF\_RESULTS\_DIR and type : run ../sub\_called\_batch\_for\_reformat\_Curie\_CD.sh to submit reformat. IMPORTANT : you have to configure the batch with the **SAME** number of processes that Specfem3D will use. One file is created by one process for one Spefem3D partition of domain.

@@

\noindent {\color{red} NOTE:} If you already know the value of the begin time and if it is already configured in 'reformat.par', you can launch the compilation of expand\_2D\_3D and reformat, AND the execution of this two programs with the single script :

@@

@@

\noindent It will do the compilation, create a traction directory here:

\noindent {\footnotesize 'EXAMPLES/coupling\_with\_EXTERNAL\_CODES/with\_AxiSEM/example\_1st\_for\_validation/DATA/AxiSEM\_tractions/1/'},

\noindent AND launch ./sub\_called\_batch\_for\_expand2D3D\_Curie\_CD.sh, AND at the end, launch \\
\noindent ./sub\_called\_batch\_for\_reformat\_Curie\_CD.sh

@@

\noindent {\color{red} BUT}, if you don't use this script or if you want to create another tractions dir, you have to create the directory yourself and launch the complication and the two run separately.

@@
